Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-20 ms.tex
I added a short description of which reference stars were selected.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
Bias correction, flat field correction and aperture centroiding was done.
The aperture centering (2D Gaussian fits) was done with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
\end{centering}
\end{figure}

@@

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
Bias correction, flat field correction and aperture centroiding was done.
The aperture centering (2D Gaussian fits) was performed with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
\end{centering}
\end{figure}

@@

Figure \ref{fig:starLabels} shows the reference stars used in the initial analysis.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/st_labels.pdf}
\caption{\shStar\ at the center and the reference stars used for the photometry.}\label{fig:starLabels}
\end{centering}
\end{figure}
